Semistochastic importance sampling of second-quantized operators in determinant space: application to multireference perturbation theory

### 2021-07-19 notes/paper.tex
New semistoch PT WIP

\section{Application to multireference perturbation theory}
We now describe

>>>>

\section{Application to multireference perturbation theory}
We now describe the application of our algorithm to multireference Epstein-Nesbet perturbation theory.

\begin{enumerate}
	\item Compute the deterministic component of the $\sigma$-vector, $\sigma^{(\epsilon)} = \sum^{(\epsilon)}_i H_{ai} c_i$, as well as its energy,
	\begin{eqnarray}
		\Delta E_{\textrm{determ.}} = \sum_a \sigma^{(\epsilon)}_a \frac{1}{E_0 - E_a} \sigma^{(\epsilon)}_a
	\end{eqnarray}
	\item Importance-sample the remaining components of the $\sigma$-vector
\end{enumerate}
